Data preparation

### 2023-10-25 procesamiento/prod_prep.Rmd
Update prod_prep.Rmd

@@

>>>>

# Thus, an EI score of -1 means complete homophily- the individual only has relationships with actors of the same “type” as they themselves are. An EI score of 1 means complete heterophily- all the alters are of a different “type” than they themselves are. Finally, an EI score of 0 means that an equal number of alters are of both the same “type” as the ego, and different types

# Group means
df1 <- df1 %>% group_by(country) %>% mutate(eindex_gm=mean(eindex,na.rm=T),
                                            homclass_gm=mean(homclass,na.rm=T))  
```

@@

# Group means
df1 <- df1 %>% group_by(country) %>% mutate(eindex2_gm=mean(eindex2,na.rm=T),
                                            homclass2_gm=mean(homclass2,na.rm=T))
```
